\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{hyperref}

\title{CS61B Lec 1}
\author{
    Sean Villegas \\
    \small \textit{Prof. Hug}
}
\date{\today}

\begin{document}

\maketitle

\noindent\textbf{\Large Notes on Course}
\begin{itemize}
    \item You need IntelliJ (because it automatically and continuously detects syntax errors)
    \item Hash tables, binary search trees, quick sort, graphs, Dijkstra’s algorithm are topics; relevant to job market
    \item Asymptotic analysis 
    \item Resizing arrays
    \item Isometry between self-balancing 2-3 trees and self-balancing red-black trees
    \item Graph Theory
    \item Polynomial vs. Non-polynomial 
        \begin{itemize}
            \item \textbf{Is every problem whose solution can be quickly verified (in polynomial time) also quickly solvable (in polynomial time)?}
        \end{itemize}
    \item B to B+ threshold is 65\% on exams, 95\% on everything else.
    \item HW01 for Java basics
    \item Lab1 for compiling and running code on machines
\end{itemize}

\vspace{1cm}
\noindent\rule{\textwidth}{0.4pt}

\noindent\textbf{\Large Java Basics, The Moral}
\begin{itemize}
    \item You need to declare what `x` is, \textit{by specifying} the data type (e.g., \textbf{int}, \textbf{String})
    \item You can specify its data type in the variable assignment or above the variable assignment.
    \item You can't assign the bound variable to another data type, even when specifying the data type you want to change it to.
    \begin{itemize}
        \item Compared to mutating variables in Python, where type checks are performed during execution.
        \item Java variable types can never change.
    \end{itemize}
\end{itemize}

\vspace{1cm}
\noindent\rule{\textwidth}{0.4pt}

\noindent\textbf{\Large Compilation vs. Interpretation}
\begin{itemize}
    \item Compilation and interpretation are two separate steps.
    \item Java will look at code and, if data types don't match, it doesn't even execute due to the compiler (i.e., static typing).
    \begin{itemize}
        \item \textbf{.class} is type checked $\rightarrow$ distributed code is safer
        \item \textbf{.class} \textit{files} are simpler for the machine to execute; distributed code is faster
        \item Protects your intellectual property 
    \end{itemize}
    \item Pros \& Cons of Static Typing
        \begin{itemize}
            \item Easy to catch certain types of errors
            \item More efficient run time
            \item Code takes more syntax to define
            \item E.g., you need to define larger functions to handle comparison of data types 
        \end{itemize}
\end{itemize}

\end{document}
